---
title: "Interactive visualizations"
---

<font size="4">**Question 1:**</font>

<font size="3">What are three households' power consumption of different appliances during time on Thanksgiving Day in 2012 (11/22/2012)? Which appliances did they use and when did they use them?</font>

<font size="4">**Question 2:**</font>

<font size="3">Which appliances did three households use most respectively on Thanksgiving Day in 2012?</font>

<font size="4">**Rationale for my design decisions:**</font>

<font size="3">I chose to create line graphs to see the trend of power consumption of different appliances during time and bar charts to see the distribution of power consumption among appliances.</font>

<font size="3">I chose to create three facets for each graphic, each facet represents a household. In a facet, a household's power consumption of different appliances during time or whole power consumption of appliances are displayed. Different colors represent different appliances in a facet and same color represents same appliance among facets.</font>

<font size="3">For plotly graphic, the interaction techniques that I used are details-on-demand and zooming. Users can obtain the details by hovering their mouse over the visualization, including appliance, householdID, time and power consumption. In addition, by selecting a small area, users can zoom in and zoom out to explore the visualization.</font>

```{r}
htmltools::includeHTML("plotly.html")
```

<font size="3">This graphic shows that except fridge and freezer, household 4 used microwave and kitchen appliances for multiple times, especially between 11:30 to 12:00. Household 5 used coffee machine at around 6:30, 12:15 and 19:00, and household 6 used kettle at around 0 o'clock. Besides, household 4 and 6 did some entertainment in the afternoon or evening and household 5 did some work in the afternoon (used PC).</font>

<font size="3">The interaction technique that I used in altair graphic is details-on-demand. By hovering the mouse over the visualization, users can obtain exact amounts of power consumption of different appliances.</font>

```{r}
htmltools::includeHTML("altair.html")
```

<font size="3">From this graphic, the power consumption of freezer of household 4 was extremely high. The power consumption of entertainment of household 4 and 6 was higher than fridge, which is an interesting finding. For household 5, the most power-consumed appliance was fridge, followed by PC.</font>

<font size="3">I considered to create visualizations using data from 06/27/12 to 01/23/13 to see the trend of power consumption during days. However, the time frame is too large that it is hard to see the details. So I chose one day, that is, Thanksgiving Day, which is a memorable day, and created visualization about this day.</font>
